---
title: "Trends on the Stock Market"
author: "Robin von Iven, Christopher Pöllinger, Benjamin Gigerl"
---

**1.1 TSLA Data Preparation**

Here we prepare the data frame for the further analysis (dplyr is needed):

```{r Data Prep}

tsla_trend_df = read.csv("TSLA Trends.csv", skip=2)
tsla_stock_df = read.csv("TSLA Stock.csv")
colnames(tsla_stock_df)[1]  = "Date_old"
tsla_stock_df$Date = as.Date(tsla_stock_df$Date_old)
tsla_max_high = max(tsla_stock_df$High)
N_tsla_stock = length(tsla_stock_df$High)

for(i in 1:N_tsla_stock) {
    tsla_stock_df$High_100[i] = tsla_stock_df$High[i]/tsla_max_high*100
}

colnames(tsla_trend_df)[1]  = "Date_old"
colnames(tsla_trend_df)[2]  = "Trends_100"
N_tsla_trend = length(tsla_trend_df$Date)

for(i in 1:N_tsla_trend) {
    tsla_trend_df$Date_new = as.Date(tsla_trend_df$Date_old[i]) + 1
}

for(i in 1:nrow(tsla_trend_df)) {
    tsla_trend_df$Date_new[i] = as.Date(tsla_trend_df$Date_old[i]) + 1
}

colnames(tsla_trend_df)[3]  = "Date"
# install.packages("dplyr")
library("dplyr")
tsla_df = inner_join(tsla_trend_df,tsla_stock_df, by="Date")

for(i in 2:nrow(tsla_df)) {
  tsla_df$Trends_100[0] = 0
  if (tsla_df$Trends_100[i] > tsla_df$Trends_100[i-1]) {
    tsla_df$Trend_increase[i] = 1
  } else {
    tsla_df$Trend_increase[i] = 0
  }
}

for(i in 2:nrow(tsla_df)) {
  if (tsla_df$High_100[i] > tsla_df$High_100[i-1]) {
    tsla_df$Stock_increase[i] = 1
  } else {
    tsla_df$Stock_increase[i] = 0
  }
}

for(i in 1:nrow(tsla_df)) {
    tsla_df$Range[i] = tsla_df$High[i] - tsla_df$Low[i]
}

tsla_df = tsla_df[, c("Date","Trends_100", "Trend_increase", "High_100", "Stock_increase", "Open", "High", "Low", "Close", "Volume", "Range")]
tsla_df

```
**1.2 TSLA Correlation Matrix**

Here we want to clarify interesting correlations by getting an overview for further analysis (corrplot is needed):
```{r Correlation Matrix}

cor_tsla_df = tsla_df[, c("Trends_100", "High_100", "Open", "High", "Low", "Close", "Volume", "Range")]
# install.packages("corrplot")
library("corrplot")
cor_tsla = cor(cor_tsla_df)
corrplot(cor_tsla)
cor_tsla

```

**1.3 TSLA Correlation Trends vs. Volume**

Here we look deeper in the correlation of trends and volume by using a plot:
```{r Corr Trends vs. Volume}

attach(tsla_df)
cor_tsla_trends_vol = cor(Trends_100, log(Volume))
cor_spear_tsla_trends_vol = cor(Trends_100, log(Volume), method="spearman")
plot(cor_tsla_df$Trends_100, log(cor_tsla_df$Volume), main="TSLA Pearson Correlation Trends vs. Volume", xlab="Trends in 100", ylab="Volume in log", pch=19); abline(lm(log(Volume)~Trends_100), col="blue", lwd=2); text(paste("Pearson Correlation:", round(cor_tsla_trends_vol, 2)), x=80, y=18.5); text(paste("Spearman Correlation:", round(cor_spear_tsla_trends_vol, 2)), x=80, y=18.3)
summary(lm(log(Volume)~Trends_100))

```

**1.4 TSLA Line Chart**

Here we get an overview over the time axis from the trends and stock highs based on 100:

```{r Line Chart}

plot(tsla_df$Date, tsla_df$Trends_100, typ="l", col="blue", main="TSLA Google Trends vs. Stock Price last 2 Years (Worldwide)", xlab="Date", ylab="Relative Change in %"); lines(tsla_df$Date, tsla_df$High_100, col="red"); legend("top", legend=c("Trends in 100", "High in 100"), col=c("blue", "red"), lty=1)

```
**1.5 TLSA Calculation of High Trends (> 50) week one and week two**

We want to clarify if the Google Trends extremes have an impact on the stock movement after one and two weeks:
```{r Calculation Strategy}

for(i in 1:nrow(tsla_df)) {
    tsla_df$Movement_one[i] = (tsla_df$Close[i+1] - tsla_df$Open[i+1])/tsla_df$Open[i+1]*100
}

for(i in 1:nrow(tsla_df)) {
    tsla_df$Movement_two[i] = (tsla_df$Close[i+2] - tsla_df$Open[i+2])/tsla_df$Open[i+2]*100
}

tsla_df_move = tsla_df[complete.cases(tsla_df), ]

print("TSLA High Trends (> 50)")

tsla_df_trend_50_one = tsla_df_move %>% filter(Trends_100 > 50)
tsla_count_trend_50_one = count(tsla_df_trend_50_one)$n
tsla_count_trend_50_negative = tsla_df_trend_50_one %>% filter(Movement_one < 0) %>% summarise(Count_negative = n())
tsla_count_trend_50_negative_one = tsla_count_trend_50_negative$Count_negative
tsla_hit_rate_trend_negative_50_one = (tsla_count_trend_50_negative_one/tsla_count_trend_50_one)*100
expected_movement_50_one = mean(tsla_df_trend_50_one$Movement_one)

print("Strategy: Trends > 50; stock going to fall; next week")
print(paste0("Occurrences: ", tsla_count_trend_50_one))
print(paste0("Favorable outcomes: ", tsla_count_trend_50_negative_one))
print(paste0("Hit rate: ", tsla_hit_rate_trend_negative_50_one))
print(paste0("Expected move: ", expected_movement_50_one))

tsla_df_trend_50_two = tsla_df_move %>% filter(Trends_100 > 50)
tsla_count_trend_50_two = count(tsla_df_trend_50_two)$n
tsla_count_trend_50_negative = tsla_df_trend_50_two %>% filter(Movement_two < 0) %>% summarise(Count_negative = n())
tsla_count_trend_50_negative_two = tsla_count_trend_50_negative$Count_negative
tsla_hit_rate_trend_negative_50_two = (tsla_count_trend_50_negative_two/tsla_count_trend_50_two)*100
expected_movement_50_two = mean(tsla_df_trend_50_two$Movement_two)

print("Strategy: Trends > 50; stock going to fall; next two week")
print(paste0("Occurrences: ", tsla_count_trend_50_two))
print(paste0("Favorable outcomes: ", tsla_count_trend_50_negative_two))
print(paste0("Hit rate: ", tsla_hit_rate_trend_negative_50_two))
print(paste0("Expected move: ", expected_movement_50_two))

tsla_df_trend_50_one_dec = tsla_df_move %>% filter(Trends_100 > 50) %>% filter(Trend_increase == 0)
tsla_count_trend_50_one_dec = count(tsla_df_trend_50_one_dec)$n
tsla_count_trend_50_negative_dec = tsla_df_trend_50_one_dec %>% filter(Movement_one < 0) %>% summarise(Count_negative = n())
tsla_count_trend_50_negative_one_dec = tsla_count_trend_50_negative_dec$Count_negative
tsla_hit_rate_trend_negative_50_one_dec = (tsla_count_trend_50_negative_one_dec/tsla_count_trend_50_one_dec)*100
expected_movement_50_one_dec = mean(tsla_df_trend_50_one_dec$Movement_one)

print("Strategy: Trends > 50; stock going to fall; Trend is lower than the prior week; next week")
print(paste0("Occurrences: ", tsla_count_trend_50_one_dec))
print(paste0("Favorable outcomes: ", tsla_count_trend_50_negative_one_dec))
print(paste0("Hit rate: ", tsla_hit_rate_trend_negative_50_one_dec))
print(paste0("Expected move: ", expected_movement_50_one_dec))

tsla_df_trend_50_two_dec = tsla_df_move %>% filter(Trends_100 > 50)  %>% filter(Trend_increase == 0)
tsla_count_trend_50_two_dec = count(tsla_df_trend_50_two_dec)$n
tsla_count_trend_50_negative_dec = tsla_df_trend_50_two_dec %>% filter(Movement_two < 0) %>% summarise(Count_negative = n())
tsla_count_trend_50_negative_two_dec = tsla_count_trend_50_negative_dec$Count_negative
tsla_hit_rate_trend_negative_50_two_dec = (tsla_count_trend_50_negative_two_dec/tsla_count_trend_50_two_dec)*100
expected_movement_50_two_dec = mean(tsla_df_trend_50_two_dec$Movement_two)

print("Strategy: Trends > 50; stock going to fall; Trend is lower than the prior week; next two weeks")
print(paste0("Occurrences: ", tsla_count_trend_50_two_dec))
print(paste0("Favorable outcomes: ", tsla_count_trend_50_negative_two_dec))
print(paste0("Hit rate: ", tsla_hit_rate_trend_negative_50_two_dec))
print(paste0("Expected move: ", expected_movement_50_two_dec))

```
**1.6 TLSA Calculation of Low Trends (< 25) week one and week two**

We want to clarify if the Google Trends extremes have an impact on the stock movement after one and two weeks:
```{r Calculation}

for(i in 1:nrow(tsla_df)) {
    tsla_df$Movement_one[i] = (tsla_df$Close[i+1] - tsla_df$Open[i+1])/tsla_df$Open[i+1]*100
}

for(i in 1:nrow(tsla_df)) {
    tsla_df$Movement_two[i] = (tsla_df$Close[i+2] - tsla_df$Open[i+2])/tsla_df$Open[i+2]*100
}

tsla_df_move = tsla_df[complete.cases(tsla_df), ]

print("TSLA Low Trends (< 25)")

tsla_df_trend_25_one = tsla_df_move %>% filter(Trends_100 < 25)
tsla_count_trend_25_one = count(tsla_df_trend_25_one)$n
tsla_count_trend_25_positive = tsla_df_trend_25_one %>% filter(Movement_one > 0) %>% summarise(Count_positive = n())
tsla_count_trend_25_positive_one = tsla_count_trend_25_positive$Count_positive
tsla_hit_rate_trend_positive_25_one = (tsla_count_trend_25_positive_one/tsla_count_trend_25_one)*100
expected_movement_25_one = mean(tsla_df_trend_25_one$Movement_one)

print("Strategy: Trends < 25; stock going to rise; next week")
print(paste0("Occurrences: ", tsla_count_trend_25_one))
print(paste0("Favorable outcomes: ", tsla_count_trend_25_positive_one))
print(paste0("Hit rate: ", tsla_hit_rate_trend_positive_25_one))
print(paste0("Expected move: ", expected_movement_25_one))

tsla_df_trend_25_two = tsla_df_move %>% filter(Trends_100 < 25)
tsla_count_trend_25_two = count(tsla_df_trend_25_two)$n
tsla_count_trend_25_positive = tsla_df_trend_25_two %>% filter(Movement_two > 0) %>% summarise(Count_positive = n())
tsla_count_trend_25_positive_two = tsla_count_trend_25_positive$Count_positive
tsla_hit_rate_trend_positive_25_two = (tsla_count_trend_25_positive_two/tsla_count_trend_25_two)*100
expected_movement_25_two = mean(tsla_df_trend_25_two$Movement_two)

print("Strategy: Trends < 25; stock going to rise; next two week")
print(paste0("Occurrences: ", tsla_count_trend_25_two))
print(paste0("Favorable outcomes: ", tsla_count_trend_25_positive_two))
print(paste0("Hit rate: ", tsla_hit_rate_trend_positive_25_two))
print(paste0("Expected move: ", expected_movement_25_two))

tsla_df_trend_25_one_inc = tsla_df_move %>% filter(Trends_100 < 25) %>% filter(Trend_increase == 1)
tsla_count_trend_25_one_inc = count(tsla_df_trend_25_one_inc)$n
tsla_count_trend_25_positive_inc = tsla_df_trend_25_one_inc %>% filter(Movement_one > 0) %>% summarise(Count_positive = n())
tsla_count_trend_25_positive_one_inc = tsla_count_trend_25_positive_inc$Count_positive
tsla_hit_rate_trend_positive_25_one_inc = (tsla_count_trend_25_positive_one_inc/tsla_count_trend_25_one_inc)*100
expected_movement_25_one_inc = mean(tsla_df_trend_25_one_inc$Movement_one)

print("Strategy: Trends < 25; stock going to rise; Trend is higher than the prior week; next week")
print(paste0("Occurrences: ", tsla_count_trend_25_one_inc))
print(paste0("Favorable outcomes: ", tsla_count_trend_25_positive_one_inc))
print(paste0("Hit rate: ", tsla_hit_rate_trend_positive_25_one_inc))
print(paste0("Expected move: ", expected_movement_25_one_inc))

tsla_df_trend_25_two_inc = tsla_df_move %>% filter(Trends_100 < 25) %>% filter(Trend_increase == 1)
tsla_count_trend_25_two_inc = count(tsla_df_trend_25_two_inc)$n
tsla_count_trend_25_positive_inc = tsla_df_trend_25_two_inc %>% filter(Movement_two > 0) %>% summarise(Count_positive = n())
tsla_count_trend_25_positive_two_inc = tsla_count_trend_25_positive_inc$Count_positive
tsla_hit_rate_trend_positive_25_two_inc = (tsla_count_trend_25_positive_two_inc/tsla_count_trend_25_two_inc)*100
expected_movement_25_two_inc = mean(tsla_df_trend_25_two_inc$Movement_two)

print("Strategy: Trends < 25; stock going to rise; Trend is higher than the prior week; next two weeks")
print(paste0("Occurrences: ", tsla_count_trend_25_two_inc))
print(paste0("Favorable outcomes: ", tsla_count_trend_25_positive_two_inc))
print(paste0("Hit rate: ", tsla_hit_rate_trend_positive_25_two_inc))
print(paste0("Expected move: ", expected_movement_25_two_inc))

```
**1.7 TSLA Bar Chart**

We want to calculate the differences of months and their increases in Trends and stock highs (lubridate is needed):
```{r Bar Chart}

#install.packages("lubridate")
library("lubridate")

for(i in 1:nrow(tsla_df)) {
    tsla_df$Month = month(tsla_df$Date[i])
}

for(i in 1:nrow(tsla_df)) {
    tsla_df$Month[i] = month(tsla_df$Date[i])
}

tsla_month = tsla_df %>% group_by(Month) %>% summarise(Count = n())
tsla_trend_increase = tsla_df %>% group_by(Month) %>% filter(Trend_increase == 1) %>% summarise(Count_Trend = n())
tsla_high_increase = tsla_df %>% group_by(Month) %>% filter(Stock_increase == 1) %>% summarise(Count_High = n())
barplot_tsla = rbind(tsla_month$Count,tsla_trend_increase$Count_Trend, tsla_high_increase$Count_High)

barplot(barplot_tsla,beside=T, names.arg=c("Jan","Feb","Mar","Apr","May","Jun","Jul","Aug","Sep","Oct","Nov","Dec"), main="TSLA Overview of Trend increases vs. Stock increases (2020 & 2021)", col=c("black", "blue", "red"), ylab="Count", xlab="Month"); legend(20,3, c("Count per Months", "Count Trend inc.", "Count Stock inc."), pch=15, col=c("black", "blue", "red"))

```
**1.8 TLSA Logistic Regression**

Here we tried out to fit a logistic regression model on Trends_100 to predict the Stock increase:
```{r Regression}

tsla_fit = glm(Stock_increase~Trends_100, data=tsla_df, family=binomial)
summary(tsla_fit)

```

\newpage

**2.1 AAPL**

To make a validation of our research, we also tried out to compute the same results for the AAPL stock:
```{r Validation}

```


# 3. Conclusion

- All our findings are documented in our Report for "Trends on the Stock Market"